\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test with Stationary Time Series

### 2023-11-08 manuscript/manuscript.tex
Wrote a little Under Size and Power

We constructed Q-Q plots of the distribution of the p-values to see if they are
normally distributed. A zoomed in plot for probabilities between 0 and 0.1, as
that is the most common range for significance levels $\alpha$.

@@

\paragraph{Power}
We must also evaluate if this method works when $H_0$ is false. We can use
the block bootstrap KS test to test if $X_t$ is generated from some other 
distribution $G$ with some unknown $\theta$. In this scenario, if the test is 
indeed powerful,
we would ideally want $\Beta$, or the probability of rejection to be 1, but we
expect it to be generally high. Again, we must try the method with different
marginal distributions to ensure that it is robust.

@@

\subsection{Precipitation in Mansfield Connecticut}
Precipitation annual maximum in inches series data was retrieved from the 
National Oceanic and Atmospheric Administration.
\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}

@@

\mc{https://www.nasdaq.com/market-activity/stocks/msft/historical}

>>>>

We constructed Q-Q plots of the distribution of the p-values to see if they are
uniformly distributed. If the distribution of the p-values is uniform, this 
indicates that the time series follows the null distribution. 
A zoomed in plot for probabilities between 0 and 0.1 is
also provided, as
that is the most common range for significance levels $\alpha$. We can also
compute the rate of rejection $\#P < \alpha$ for different values of
$\alpha$, as well as a confidence interval
for this proportion.

@@

\paragraph{Power}
We must also evaluate if this method works when $H_0$ is false. We can use
the block bootstrap KS test to test if $X_t$ is generated from some other 
distribution $G$ with some unknown $\theta$. In this scenario, if the test is 
indeed powerful,
we would ideally want $\beta$, or the probability of rejection to be 1, but we
expect it to be generally high. Again, we must try the method with different
marginal distributions to ensure that it is robust.
We would then expect the distribution of p-values to be non-normal, and the rate
of $\#P < \alpha$ to be high, meaning a higher density of low p-values.

If we can show that the test correctly fails to reject $H_0$ under the null
distribution, and correctly rejects $H_0$ for an alternate distribution, we can
state tht the method works.

@@

\subsection{Precipitation in Mansfield Connecticut}
Precipitation annual maximum in inches series data was retrieved from the 
National Oceanic and Atmospheric Administration.
%\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}

@@

%\mc{https://www.nasdaq.com/market-activity/stocks/msft/historical}
